Lyman-alpha spectra from rotating outflows

### 2018-03-27 paper/paper.tex
plots

\begin{figure}
	\begin{center}
		\includegraphics[width=0.45\textwidth]{./figures/discussion/doppler}
	\end{center}
	\caption{\textbf{Doppler Shift:} We fix $\vout=25$\kms, $\vrot=100$\kms, $\tauh=10^5$.
		\label{fig:doppler}}
\end{figure}

@@

In this appendix we show more \lya spectra in the Figures 
\ref{fig:varying_rotation} and \ref{fig:varying_outflow} 
with the complete range of combinations of \vrot and \vout.

>>>>

\begin{figure}
	\begin{center}
		\includegraphics[width=0.48\textwidth]{./figures/discussion/doppler}
	\end{center}
	\caption{\textbf{Doppler Shift:} We fix $\vout=25$\kms, $\vrot=100$\kms, $\tauh=10^5$.
		\label{fig:doppler}}
\end{figure}

@@

In this appendix we show \lya spectra with fixed \vout (Fig. \ref{fig:varying_rotation_small})
and fixed \vrot (Fig. \ref{fig:varying_outflow_small}). For a larger set of spectra with the
same fixed \vout and \vrot refer to Fig. \ref{fig:varying_rotation} and Fig. \ref{fig:varying_outflow} 
respectively.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/appendix/varying_rotation_small}
	\end{center}
	\caption{\textbf{Caption:} $\vout=50$\kms.
		\label{fig:varying_rotation_small}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/appendix/varying_outflow_small}
	\end{center}
	\caption{\textbf{Caption:} $\vrot=50$\kms.
		\label{fig:varying_outflow_small}}
\end{figure*}
